Prediction of 2024 US election ...

### 2024-11-03 paper/paper.qmd
delete unnecessary data

library(tidyverse)
library(palmerpenguins)
library(here)
library(tibble)
library(knitr)
library(arrow)
library(rstanarm)
library(brms)
library(dplyr)
library(lubridate)
library(gridExtra)
library(Matrix)
library(rstan)

>>>>

library(tidyverse)
library(here)
library(tibble)
library(knitr)
library(arrow)
library(rstanarm)
library(brms)
library(dplyr)
library(lubridate)
library(gridExtra)
library(Matrix)
library(rstan)

light_blue <- "#ADD8E6"
dark_blue <- "#6688CC"
light_red <- "#FF7777"
dark_red <- "#B22222"
purple <- "#9370DB"
